\NeedsTeXFormat{LaTeX2e}

\documentclass[12pt]{article}
\usepackage[letterpaper,portrait, margin=1in]{geometry}
\usepackage{booktabs, pgfplots, bm, multirow, amsmath, wrapfig, gensymb, graphicx}
\pgfplotsset{width=11cm,compat=1.9}
\renewcommand{\arraystretch}{1.5}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{indentfirst}



\begin{document}
\input{Lab 4 Cover Page.tex}
\newpage
\tableofcontents
\newpage
\section{Purpose}
In this lab, Bessel's Method will be used to determine the focal lengths of two converging lenses. 
The focal length of each lens is approximated using the thin lens equation (Eq. 1). 
Here, the lenses are convex, meaning that $f$ is positive.
This approximate focal length is used to determine the distance between the source and the screen $(D)$. 
$D$ must be sufficiently large so that the light rays will converge and form a real image. 
If $D$ is too small, a virtual image will be formed, which only exists within the brain.
A clear image is formed by each lens in two positions, the difference of which $(d)$ is used in Bessel's Method to calculate the focal lengths.
The angular magnification of the two lenses will then be calculated and used to construct a simple telescope, which is used to test the expected magnification value.  
\newpage
\section{Data}
\input{tables.tex}
\newpage
\section{Calculations}
\subsection*{Part A: Bessel's Method for Determining Focal Length}
\noindent \textbf{1. Thin Lens Equation}\[\frac{1}{p}+\frac{1}{i}=\frac{1}{f}\]
    Where $p$ is the distance between the source and the lens, $i$ is the distance between the image and the lens, and $f$ is the focal length of the lens. \\
\textbf{2. Focal Length of Lens $\bm{({f})}$}\[f=\frac{D^2-d^2}{4D}\]
    Initially, the focal length of each lens is approximated, which allows us to find our value for $D$, the distance between the source and screen. $D$ must be greater than $4f$, where $f$ is our approximate focal length. Each lens has two positions where a sharp image is displayed, and the difference between these two positions provides our $d$ value. From there, an accurate focal length can be determined for each lens using this equation.
    The error of the mean values were propagated through this calculation using the following equations.
\subsubsection*{Error Propagation:}
    \noindent\textbf{2.1 Partial Derivative of Eq. 2 w.r.t $\bm d$}\[\frac{\partial f}{\partial d}=\dfrac{-d}{2D}\]
    \textbf{2.2 Partial Derivative of Eq. 2 w.r.t $\bm D$} \[\frac{\partial f}{\partial D}=\dfrac{D^2+d^2}{4D^2}\]
    Each of these partial derivatives are used in the final calculation of the total error associated with $f.$ Because $d$ and $D$ are dependent variables we use the following equation to find the total error.\\
    \textbf{2.3 Total Error Associated with the Focal Length $\bm{(f)}$}\[\delta f =\left|\frac{\partial f}{\partial d}\delta d\right|+\left|\frac{\partial f}{\partial D}\delta D\right|\]
    The error associated with the mean values were calculated (shown in Tables 6 and 7). This provides our final error associated with $f$.\\
\\\textbf{3. Angular Magnification $\bm{(m_\theta)}$}\[m_\theta=-\frac{f_{obj}}{f_{eye}}\]
    We proceed to calculate the angular magnification $(m_\theta)$, which relies on the focal lengths of both lenses. $f_{obj}$ is the focal length of the objective lens, which is the lens with a longer focal length. The lens with the short focal length acts as the eyepiece, $f_{eye}.$ The total error of $m_\theta$ is found using the following equations.
\subsubsection*{Error Propagation:}
    \noindent\textbf{3.1 Partial Derivative of Eq. 3 w.r.t $\bm f_{obj}$}\[\frac{\partial m_\theta}{\partial f_{obj}}=\dfrac{-1}{f_{eye}}\]
    \textbf{3.2 Partial Derivative of Eq. 3 w.r.t $\bm f_{eye}$} \[\frac{\partial m_\theta}{\partial f_{eye}}=\dfrac{f_{obj}}{f_{eye}^2}\]
    Each of these partial derivatives are used in calculating the total error in the following equation. Both $f_{eye}$ and $f_{obj}$ are independent, which allows us to use the following equation.\\
    \textbf{3.3 Total Error Associated with the Angular Magnification $\bm{({m_\theta})}$}\[\delta m_\theta =\sqrt{\left(\frac{\partial m_\theta}{\partial f_{obj}}\delta f_{obj}\right)^2+\left(\frac{\partial m_\theta}{\partial f_{eye}}\delta f_{eye}\right)^2}\]
    As in Equation 1.3, this equation gives us the total error associated with $(m_\theta)$, shown in the results section (Table 8).
\newpage
\section{Results}
\input{results.tex}
\newpage
\section{Conclusion}
Using Bessel's method, a focal length for Lens F1 was calculated to be $5.00\pm0.03$ cm, and $9.83\pm0.03$ cm for Lens C. 
These calculated focal lengths provided a magnification factor of $1.965\pm0.014$. 
Based on the calculated magnification factor and focal lengths, a simple telescope was constructed, which provided an experimental magnification factor of $2.11\pm0.05$. 
Although these magnification factors do not lie in the same error range, further experimental measurements could provide more similar experimental and theoretical magnification factors.
The difference between the experimental and theoretical values can b attributed to human error, as described above. 
If error could be reduced, Bessel's Method will provide for more accurate focal length and magnification factor values.
\newpage
\section{Questions}
\subsection*{1. Derive the equation $\bm{f=\frac{D^2-d^2}{4D}}$ and explain why we need the subsidiary condition $\bm{D>4f}$.}
\noindent Starting with the thin lens equation (Eq. 1), \[\frac{1}{p}+\frac{1}{i}=\frac{1}{f}\] Since $i$ is the distance between the image and the lens, we can rewrite the equation, \[i=D-p\]\[\frac{1}{p}+\frac{1}{D-p}=\frac{1}{f}\] 
We then rewrite as the following equation \[Df=pD-p^2\] which can be solved via the quadratic equation \[p=\frac{D\pm\sqrt{D^2-4Df}}{2}\]
Note here that if $D>4f$ the discriminant is positive, meaning that for all other cases an imaginary answer will be given for $p$. We can denote the two positions of $p$ by $d$, which is the difference between the two positions
\[d=\frac{D+\sqrt{D^2-4Df}}{2}-\frac{D-\sqrt{D^2-4Df}}{2}=\sqrt{D^2-4fD}\]
Using this value of $d$, we can solve for $f$ \[d^2=D^2-4fD\]\[D^2-d^2=4fD\]
\[\boxed{f=\frac{D^2-d^2}{4D}}\]
\newpage
\subsection*{2. To get the approximate focal length of the lens we approximated the distance from the lens to the source to be infinite when it was actually finite (but large). Use the thin lens equation to show that this will slightly overestimate the focal length of the lens.}
\noindent Starting with the thin lens equation (Eq. 1), \[\frac{1}{p}+\frac{1}{i}=\frac{1}{f}\]
Since we take $p\rightarrow\infty$, $\frac{1}{p}\rightarrow0$, which provides us with the following relationship\[0+\frac{1}{i}=\frac{1}{f}\Rightarrow f=i\]
Substituting back into the thin lens equation gives \[\frac{1}{p}+\frac{1}{f}=\frac{1}{f}\] which implies that a finite $p$ value will make for a slight overestimation of the focal length.
\end{document}